Adversarial Training of Neural Networks\\ against Systematic Uncertainty

### 2016-08-29 tex/paper.tex
L_r also depends on theta_f
save

In this work, we repurpose adversarial training as a means to constraint the
predictive model $f$ in order to satisfy Eqn.~\ref{eqn:criterion}. In
particular, we pit $f$ against an adversary classifier $r(\cdot ;
\theta_r) : \mathbb{R} \mapsto \Lambda$ of parameters $\theta_r$ and
associated loss ${\cal L}_r(\theta_r)$.
Assuming that $\Lambda$ defines a finite family of nuisance values $\lambda_l$ (for $l=1, \dots, |\Lambda|$),
this model takes as input realizations of $f(X; \theta_f)$
and produces as output probability estimates $r(f(X; \theta_f); \theta_r)_l = \hat{p}(\lambda_l| f(X; \theta_f)) $
that $f(X; \theta_f)$ is generated from the nuisance value $\lambda_l$. If $p(f(X; \theta_f)|\lambda)$ varies with $\lambda$,
then the corresponding correlation can be captured by $r$. By contrast, if
$p(f(X; \theta_f)|\lambda)$ is invariant with $\lambda$, as we require, then $r$
should perform poorly and be close to random guessing. Training $f$ such that it additionally minimizes the performance of $r$
therefore acts as a regularization towards Eqn.~\ref{eqn:criterion}.

As for generative adversarial networks, we propose to
train $f$ and $r$ simultaneously, which we carry out by considering
the value function
\begin{equation}
    E(\theta_f, \theta_r) = {\cal L}_f(\theta_f) - {\cal L}_r(\theta_r)
\end{equation}
that we optimize by finding the saddle point $(\smash{\hat\theta_f}, \smash{\hat\theta_r})$ such that
\begin{align}
    \smash{\hat\theta_f} &= \arg \min_{\theta_f} E(\theta_f, \smash{\hat\theta_r}), \label{eqn:min_thetaf} \\
    \smash{\hat\theta_r} &= \arg \max_{\theta_r} E(\smash{\hat\theta_f}, \theta_r) \label{eqn:max_thetar}.
\end{align}
The adversarial training procedure to obtain $(\smash{\hat\theta_f},
\smash{\hat\theta_r})$ is formally presented in
Algorithm~\ref{alg:adversarial-training} in the case of $f$ being a classifier
and of using the log-loss for both ${\cal L}_f$ and ${\cal L}_r$. The algorithm
consists in using stochastic gradient descent alternatively to optimize
Eqn.~\ref{eqn:min_thetaf} and \ref{eqn:max_thetar}.

>>>>

In this work, we repurpose adversarial training as a means to constraint the
predictive model $f$ in order to satisfy Eqn.~\ref{eqn:criterion}. In
particular, we pit $f$ against an adversary classifier $r(\cdot ;
\theta_r) : \mathbb{R} \mapsto \Lambda$ of parameters $\theta_r$ and
associated loss ${\cal L}_r(\theta_f, \theta_r)$.
Assuming that $\Lambda$ defines a finite family of nuisance values $\lambda_l$ (for $l=1, \dots, |\Lambda|$),
this classifier takes as input realizations of $f(X; \theta_f)$, for the current value $\theta_f$ of $f$ parameters,
and produces as output probability estimates $r(f(X; \theta_f); \theta_r)_l = \hat{p}(\lambda_l| f(X; \theta_f)) $
that $f(X; \theta_f)$ is generated from the nuisance value $\lambda_l$. If $p(f(X; \theta_f)|\lambda)$ varies with $\lambda$,
then the corresponding correlation can be captured by $r$. By contrast, if
$p(f(X; \theta_f)|\lambda)$ is invariant with $\lambda$, as we require, then $r$
should perform poorly and be close to random guessing. Training $f$ such that it additionally minimizes the performance of $r$
therefore acts as a regularization towards Eqn.~\ref{eqn:criterion}.

As for generative adversarial networks, we propose to
train $f$ and $r$ simultaneously, which we carry out by considering
the value function
\begin{equation}
    E(\theta_f, \theta_r) = {\cal L}_f(\theta_f) - {\cal L}_r(\theta_f, \theta_r)
\end{equation}
that we optimize by finding the saddle point $(\smash{\hat\theta_f}, \smash{\hat\theta_r})$ such that
\begin{align}
    \smash{\hat\theta_f} &= \arg \min_{\theta_f} E(\theta_f, \smash{\hat\theta_r}), \label{eqn:min_thetaf} \\
    \smash{\hat\theta_r} &= \arg \max_{\theta_r} E(\smash{\hat\theta_f}, \theta_r) \label{eqn:max_thetar}.
\end{align}
The adversarial training procedure to obtain $(\smash{\hat\theta_f},
\smash{\hat\theta_r})$ is formally presented in
Algorithm~\ref{alg:adversarial-training} in the case of $f$ being a classifier
and of the cross-entropy loss for both ${\cal L}_f$ and ${\cal L}_r$. The algorithm
consists in using stochastic gradient descent alternatively to optimize
Eqn.~\ref{eqn:min_thetaf} and \ref{eqn:max_thetar}.
